---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# polylabelr

<!-- badges: start -->
[![R-CMD-check](https://github.com/jolars/polylabelr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jolars/polylabelr/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/polylabelr)](https://cran.r-project.org/package=polylabelr)
[![Codecov test coverage](https://codecov.io/gh/jolars/polylabelr/graph/badge.svg)](https://app.codecov.io/gh/jolars/polylabelr)
<!-- badges: end -->

**polylabelr** is an R wrapper for the 
[polylabel package](https://github.com/mapbox/polylabel)
from [Mapbox](https://www.mapbox.com/). It currently contains a single function,
`poi()` that finds the *pole of inaccessibility* of a polygon, which usually
makes for a good place to put a label on a polygon---hence the name.

## Usage

```{r}
# a concave polygon
x <- c(0, 4, 1, 6, 7, 7, 0, 0)
y <- c(0, 0, 1, 2, 1, 3, 2, 0)

# locate the pole of inaccessibility
p <- polylabelr::poi(x, y, precision = 0.01)

plot.new()
plot.window(range(x, na.rm = TRUE), range(y, na.rm = TRUE), asp = 1)
polypath(x, y, col = "grey", border = FALSE)
points(p)
```

## Installation

### CRAN version

```{r, eval = FALSE}
install.packages("polylabelr")
```

### Development version

```{r, eval = FALSE}
remotes::install_github("jolars/polylabelr")
```

## Modifications

The source code from [geometry.hpp](https://github.com/mapbox/geometry.hpp/) 
has been modified slightly by removing the use of some GCC diagnostic
pragmas that caused warnings in R CMD check.


## Versioning

**polylabelr** uses [semantic versioning](https://semver.org/).
